Generating Images from Captions\\ with Attention

### 2015-11-09 supp.tex
a

\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\includegraphics[width=0.99\textwidth]{figures/new/mnist/test3.pdf}\quad
%
\end{center}
\caption{Examples of generating $60 \times 60$ MNIST images corresponding to respective captions. The captions on the \textbf{left column} were part of the training set. The digits described in the captions on the \textbf{right column} were hidden during training for the respective configurations.}
\label{fig:figmnist}
\vspace{-0.3cm}
\end{figure}

@@

Each parameter in alignDRAW was initialized by sampling from a Gaussian distribution with 
mean $0$ and standard deviation $0.01$. 
The model was trained using \textit{RMSprop} with an initial learning rate of $0.001$. 
For the Microsoft COCO task, we trained our model for $18$ epochs. The learning rate was 
reduced to $0.0001$ after $11$ epochs.
For the MNIST with Captions task, the model was trained for 150 epochs and the 
learning rate was reduced to $0.0001$ after 110 epochs. During each epoch, randomly created $10000$ training samples were used for training.
The norm of the gradients was clipped at $10$ during training 
to avoid the exploding gradients problem.

@@

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c | c c c c c c}
\hline
%\hline
 & & \multicolumn{3}{c}{\textbf{alignDRAW Model}}  & &  \\
\hline
Task & \#glimpses & Inference  & Generative  & Latent & Read Size & Write Size\\
     & \ T & Dim of $h^{infer}$ & Dim of $h^{gen}$  & Dim of $Z$  & $p$ & $p$\\
\hline
MS COCO & 32 & 550 & 550 & 275 & 9 & 9\\
MNIST   & 32 & 300 & 300 & 150 & 8 & 8\\
\end{tabulary}
\caption{The architectural configurations of alignDRAW models.}
\label{tab:drawhyper}
\end{center}
%\vspace{-0.3cm}
\end{table}

@@

\begin{table}[!h]
\begin{center}
\begin{tabulary}{\linewidth}{c | c c c c}
\hline
Model & Train LL & Valid LL & Test LL & Test LL (after sharpening)\\
\hline
skipthoughtDRAW & -1794.29 & -1797.41 & -1791.37 & -2045.84 \\
noalignDRAW & -1792.14 & -1796.94 & -1791.15 & -2051.07 \\
alignDRAW & -1792.15 & -1797.24 & -1791.53 & -2042.31
\end{tabulary}
\caption{The lower bound on the average test log-probabilities of conditional DRAW models, trained on the Microsoft COCO dataset.}
\label{tab:nll}
\end{center}
\end{table}

@@

%\vspace{-0.1in}

>>>>

\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\includegraphics[width=0.99\textwidth]{figures/new/mnist/test3.pdf}\quad
\end{center}
\caption{Examples of generating $60 \times 60$ MNIST images corresponding to respective captions. The captions on the \textbf{left column} were part of the training set. The digits described in the captions on the \textbf{right column} were hidden during training for the respective configurations.}
\label{fig:figmnist}
\vspace{-0.3cm}
\end{figure}

@@

Each parameter in alignDRAW was initialized by sampling from a Gaussian distribution with 
mean $0$ and standard deviation $0.01$. 
The model was trained using \textit{RMSprop} with an initial learning rate of $0.001$. 
For the Microsoft COCO task, we trained our model for $18$ epochs. The learning rate was 
reduced to $0.0001$ after $11$ epochs.
For the MNIST with Captions task, the model was trained for 150 epochs and the 
learning rate was reduced to $0.0001$ after 110 epochs. During each epoch, 
randomly created $10,000$ training samples were used for learning. 
The norm of the gradients was clipped at $10$ during training 
to avoid the exploding gradients problem.

@@

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c | c c c c c c}
\hline
 & & \multicolumn{3}{c}{\textbf{alignDRAW Model}}  & &  \\
\hline
Task & \#glimpses & Inference  & Generative  & Latent & Read Size & Write Size\\
     & \ T & Dim of $h^{infer}$ & Dim of $h^{gen}$  & Dim of $Z$  & $p$ & $p$\\
\hline
MS COCO & 32 & 550 & 550 & 275 & 9 & 9\\
MNIST   & 32 & 300 & 300 & 150 & 8 & 8\\
\end{tabulary}
\caption{The architectural configurations of alignDRAW models.}
\label{tab:drawhyper}
\end{center}
\end{table}

@@

\begin{table}[!h]
\begin{center}
\begin{tabulary}{\linewidth}{c | c c c c}
\hline
Model & Train & Validation  & Test  & Test  (after sharpening)\\
\hline
skipthoughtDRAW & -1794.29 & -1797.41 & -1791.37 & -2045.84 \\
noalignDRAW & -1792.14 & -1796.94 & -1791.15 & -2051.07 \\
alignDRAW & -1792.15 & -1797.24 & -1791.53 & -2042.31
\end{tabulary}
\caption{The lower bound on the average test log-probabilities of conditional DRAW models, trained on the Microsoft COCO dataset.}
\label{tab:nll}
\end{center}
\end{table}

@@
